Body Image and Trikafta

### 2024-06-21 Emily Muther/body_image_trikafta.qmd
trikafta adherence

>>>>

## Adherence

```{r}
#| label: adherence
df %>%
  select(contains("Adherence"),FRS_Category) %>%
  mutate(PercentAdherence=as.numeric(sub("%","",as.character(PercentAdherence)))) %>%
  tbl_summary(
    by = "FRS_Category",
    type = list("PercentAdherence"~"continuous"),
    missing_text = "(Missing)"
  ) %>%
  add_overall() %>%
  add_p() %>%
  separate_p_footnotes()
```
